\chapter{Crypto.Symmetric.Blockcipher}\label{Blockcipher}
In this generic package a block cipher is generated based on the
symmetric algorithms (Chapter \ref{Algorithm}). Users should always
use the API of the package, where a secure application can be ensured.
When one encrypts two identical plaintext blocks $P_1=P_2$ with the
same key, then two identical ciphertext blocks $C_1=C_2$ will be
produced. Thus the ciphertext can provide information about the
structure of the plaintext.
\section{API}
The API of a block cipher is mainly made of the following parts:
\begin{itemize}
\item One procedure \texttt{Prepare\_Key()}: it assigns a value as the
  cipher key.
\begin{lstlisting}{}
  procedure Prepare_Key(Key : in Key_Type);
\end{lstlisting}
\item One procedure \texttt{Encrypt()}: the procedure encrypts a
  plaintext block (with a key) to a ciphertext block.
\begin{lstlisting}{}
  procedure Encrypt(Plaintext: in Block; Ciphertext : out Block);
\end{lstlisting}
\item One procedure \texttt{Decrypt()}: the procedure recovers a
  ciphertext block (with a key) to a plaintext block.
\begin{lstlisting}{}
  procedure Decrypt(Ciphertext: in Block; Plaintext : out Block);
\end{lstlisting}
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Generic Part}
\begin{lstlisting}{}
  type Block is private;
  type Key_Type is private;
  type Cipherkey_Type is private;
  with procedure Prepare_Key(Key       : in  Key_Type;
                             Cipherkey : out Cipherkey_Type) is <>;
  with procedure Encrypt(Cipherkey  : in  Cipherkey_Type;
                         Plaintext  : in  Block;
                         Ciphertext : out Block) is <>;
  with procedure Decrypt(Cipherkey  : in  Cipherkey_Type;
                         Ciphertext : in  Block;
                         Plaintext  : out Block) is <>;
  with function To_Key_Type
                (B : Crypto.Types.Bytes) return Key_Type is <>;
  with function To_Block_Type
                (B : Crypto.Types.Bytes) return Block is <>;
  with function Block_To_Bytes
                (B : Block) return Crypto.Types.Bytes is <>;
\end{lstlisting}
Since they are generic, they should be specified at first.\\

\noindent\textbf{Exceptions:}
\begin{itemize}
\item In the function \texttt{To\_Key\_Type()}, if the size of the
  data does not match the size of the key
  type:\quad\texttt{Constraint\_Error}.
\item In the function \texttt{To\_Block\_Type()}, if the size of the
  data does not match the size of the
  block:\quad\texttt{Constraint\_Error}.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent\textbf{Remarks.}
Users don't need to generate block ciphers from the symmetric
algorithms every time. They can use the following already built
blockciphers in the ACL.
\begin{itemize}
\item \texttt{Crypto.Symmetric.Blockcipher\_AES128/AES192/AES256}
\item \texttt{Crypto.Symmetric.Blockcipher\_Blowfish128}
\item \texttt{Crypto.Symmetric.Blockcipher\_Noob64}
\item \texttt{Crypto.Symmetric.Blockcipher\_Serpent256}
\item \texttt{Crypto.Symmetric.Blockcipher\_TripleDES}
\item \texttt{Crypto.Symmetric.Blockcipher\_Twofish128/Twofish192/Twofish256}
\end{itemize}
