\chapter{Crypto.Symmetric.Oneway\_Blockcipher}\label{Oneway-Blockcipher}
With generic packages we can also generate a one-way block cipher with help of a one-way symmetric algorithm (chapter \ref{OnewayAlgo}) or a hash function (chapter \ref{Hash}).

By the one-way block cipher which is based on hash functions, the length of the key (at least 256 bits) will be chosen so that it is impossible to search the complete key space. For instance of an irreversible counter of 219 bits, it demands min. $10^{51}erg.$ to traverse all states, it corresponds the energy to deliver a typical supernova. Thus to traverse all states of a 256 bits counter, it needs min. energy of 64 milliarde supernoven. But the energy output of our sun is just only $1,21*10^{41}erg.$ one year \cite{DBLP:books/daglib/0021657}. So that such a one-way block cipher is as (in-)secure as the basic hash functions.
\section{Generic Part}
\begin{lstlisting}{}
  generic
    type Block is private;
    type Key_Type is private;
    type Cipherkey_Type is private;
    with procedure Prepare_Key(Key       : in  Key_Type;
                               Cipherkey : out Cipherkey_Type);
    with procedure Encrypt(Cipherkey  : in  Cipherkey_Type;
                           Plaintext  : in  Block;
                           Ciphertext : out Block);
    with function To_Block_Type (B : Crypto.Types.Bytes) 
    							    return Block is <>;
    with function Block_To_Bytes(B : Block) 
    							    return Crypto.Types.Bytes is <>;
\end{lstlisting}
The types should be specified before use. Furthermore, the API should be identical to the one-way algorithms.\\
\section{API}
The API of a one-way block cipher is made as in the following:
\begin{itemize}
\item One procedure \texttt{Prepare\_Key()}: it assigns a value as the cipher key.
\begin{lstlisting}{}
  procedure Prepare_Key(Key : in Key_Type);
\end{lstlisting}
\item One procedure \texttt{Encrypt()}: it encrypts a plaintext block to a ciphertext block under the cipher key.
\begin{lstlisting}{}
  procedure Encrypt(Plaintext: in Block; Ciphertext: out Block);
\end{lstlisting}
\item One function \texttt{To\_Block()}: to transform data of bytes into a block.
\begin{lstlisting}{}
  function To_Block(Byte_Array: Crypto.Types.Bytes) return Block;
\end{lstlisting}
\textbf{Exception:}\\ 
If the size of the data does not match the size of the block:\quad\texttt{Constraint\_Error}.
\item One function \texttt{To\_Bytes()}: to transform a block into bytes.
\begin{lstlisting}{}
  function To_Bytes(B : Block) return Crypto.Types.Bytes;
\end{lstlisting}
\end{itemize}
\section{Use in Example}
\begin{lstlisting}{}
  with Crypto.Types; use Crypto.Types;
  with Crypto.Symmetric.Oneway_Blockcipher;
  with Crypto.Symmetric.Algorithm.TripleDES.Oneway;
  procedure Generic_Oneway_TripleDES is
  use Crypto.Symmetric.Algorithm.TripleDES.Oneway;
    package Oneway_TripleDES is
      new Crypto.Symmetric.Oneway_Blockcipher
      (Block          => B_Block64,
       Key_Type       => B_Block192,
       Cipherkey_Type => Cipherkey_Oneway_TDES,
       Prepare_Key    => Prepare_Oneway_Key,
       Encrypt        => Encrypt_Oneway);
  begin
    ...
  end Generic_Oneway_TripleDES;
\end{lstlisting}
\textbf{Remarks:}\\
Users don't need to generate one-way block cipher every time. There exist already one-way block ciphers.
\begin{itemize}
\item \texttt{Crypto.Symmetric.Oneway\_Blockcipher\_AES128}
\item \texttt{Crypto.Symmetric.Oneway\_Blockcipher\_AES192}
\item \texttt{Crypto.Symmetric.Oneway\_Blockcipher\_AES256}
\item \texttt{Crypto.Symmetric.Oneway\_Blockcipher\_Blowfish128}
\item \texttt{Crypto.Symmetric.Oneway\_Blockcipher\_Serpent256}
\item \texttt{Crypto.Symmetric.Oneway\_Blockcipher\_TripleDES}
\item \texttt{Crypto.Symmetric.Oneway\_Blockcipher\_Twofish128}
\item \texttt{Crypto.Symmetric.Oneway\_Blockcipher\_Twofish192}
\item \texttt{Crypto.Symmetric.Oneway\_Blockcipher\_Twofish256}
\item \texttt{Crypto.Symmetric.Oneway\_Blockcipher\_Whirlpool}
\item \texttt{Crypto.Symmetric.Oneway\_Blockcipher\_SHA1}
\item \texttt{Crypto.Symmetric.Oneway\_Blockcipher\_SHA256}
\item \texttt{Crypto.Symmetric.Oneway\_Blockcipher\_SHA384}
\item \texttt{Crypto.Symmetric.Oneway\_Blockcipher\_SHA512}
\end{itemize}
